Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/shell-model.tex
Proposal of an alternative start of the shell model section.
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@356 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

>>>>

\stefan{Alternative start of this section: In congenital heart defect (CHD) corrective surgeries blood vessels respond to plastic interventions with a certain amount of deformation. Surgeons try to find an optimal approach to correct defects with a minimum of deformations and collisions that would have unnecessary negative impact on blood flow or that may lead to problems during growth of the patient. To be able to predict results for different surgical approaches a physical approriate model of blood vessels is mandatory. Furthermore, computation time of simulations must be low enough to enable interactive and usable planning software. Options on the choice of model are limited. Mass-spring models allow for fast computation but do not correlate to a physical accurate representation of reality and therefore are inappropriate for predictive simulations. On the contrary, simulation models based on the formulation of finite elements, either 3-dimensional elements or thin shell elements, are commonly used when high physical accuracy is required but are well known to be computationally expensive. The hybrid blood vessel model of REF strikes a balance but is too constrained to be used as a truly universal approach for all kinds of surgical procedures used in CHD corrective surgery. We propose a model based on thin shell elements that still allows for fast computation with a reasonable number of elements.}
